% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Roman Gonzalez}
% \address used twice to have two lines of address
\address{7707 Arthur Av. Burnaby, BC. Canada}
\address{+1 (604) 728-4864}
 
\begin{resume}
 
\section{SKILLS} 
  \begin{list}{\labelitemi}{\leftmargin=1em}
    \item Proficient level on the Ruby Programming Language
    \item Competent level on the Java Programming Language
    \item Proficient level on Ruby Web Frameworks and Web Technologies
    \item Competent level on Collaborative Development using GIT and Subversion 
    \item Competent level on the use of Design Patterns
    \item Knowledge of *nix system architecture
    \item Basic Knowledge of the Haskell Programming Language
    \item Basic Knowledge of Python Programming Language
    \item Basic Knowledge of Distributed Applications, Database and Networks
  \end{list}

\section{LANGUAGES}
  \textbf{Spanish} -- Mother's Language \\
  \textbf{English} -- Advanced and Technical \\
  \textbf{German}  -- Beginner

\section{EDUCATION}
  {\sl B.S. in Computer Science} \hfill \textbf{Nov 2002 - Jul 2008} \\
  {\sl Universidad Central de Venezuela (UCV) } \\
  {\sl Specializing in Parallel and Distributed Computing} \\
  \begin{list}{\labelitemi}{\leftmargin=1em}
    \item Developed simple applications using C programming language and MPI
    \item Developed applications using CORBA with Python (Fnorb), including SOAP for Web Services 
          and PSP with mod\_python for web interface
    \item Developed Web Applications using Java and J2EE with Struts and Hibernate Frameworks
    \item Developed Web Applications using Ruby and Ruby on Rails
  \end{list}
  {\sl IBM Ace Professional certificate} \hfill \textbf{May 2004 - May 2005} \\
  {\sl IBM Venezuela. Specialized in Web Application Development and e-Business.}
  
\section{TEACHING}
  {\sl Instructional Student Assistant} \hfill \textbf{Spring 2006} \\
  \newline
  Data Structures and Algorithms, Computer Science School, Universidad Central de Venezuela. Caracas, Venezuela.

\section{AWARDS}
  {\sl Honorable Mention} -- ACM International Collegiate Programming Contest 31th World Finals. 
  Tokyo, Japan. \textbf{March 2007} \\
  \newline
  {\sl Champion, Venezuela and Colombia Region} -- ACM International Collegiate Programming Contest, 9th South 
  American Region Contest. Cumaná, Venezuela. \textbf{Nov 2006} \\
  \newline
  {\sl Champion, UCV} -– 12th ACM Local Programming Contest, Universidad Central de Venezuela (UCV). 
  Caracas, Venezuela. \textbf{Jul 2006} \\
  \newline
  {\sl Champion, UCAB} –- 8th ACM Local Programming Contest, Universidad Católica Andrés Bello (UCAB). 
  Caracas, Venezuela. \textbf{Jun 2006} \\
  \newline
  {\sl Honorable Mention} -– ACM International Collegiate Programming Contest, 30th World Finals. 
  San Antonio, Texas, United States. \textbf {Apr 2006} \\
  \newline
  {\sl Certificate of Achievement} –- Upsilon Pi Epsilon Honor Society in the Computing \& Information Disciplines. 
  San Antonio, Texas, United States. \textbf {Apr 2006} \\
  \newline
  {\sl Champion, Venezuela} – ACM International Collegiate Programming Contest, 8th South American Region 
  Contest. Caracas, Venezuela. \textbf {Nov 2005} \\
  \newline
  {\sl Champion, UCV} – 11th ACM Local Programming Contest, Universidad Central de Venezuela (UCV). 
  Caracas, Venezuela. \textbf {Jul 2005} \\
  \newline
  {\sl Champion, UCAB} – 7th ACM Local Programming Contest, Universidad Católica Andrés Bello (UCAB)
  Caracas, Venezuela. \textbf {Jun 2005} \\

\section{OPEN SOURCE}
  \begin{list}{\leftmargin=1em}
    \setlength{\itemsep=30em}
    \item \textbf{\href{http://www.github.com/roman/walruz}{walruz}} -- Ruby authorization library for the 
    development of complex authorization architectures using composition of simple policies
    \item \textbf{\href{http://github.com/roman/warden\_oauth}{warden\_oauth}} -– This a Warden extension that 
    provides easy setup for authentication using the OAuth protocol
    \item \textbf{\href{http://github.com/roman/merb\_cucucmber}{merb\_cucumber}} -– Co-authored with David Leal, 
    this is a gem that provides an easy integration with the Cucumber test framework
    \item \textbf{\href{http://github.com/roman/rots}{rots (Ruby OpenID Test Server)}} -– A gem that provides 
    an easy interface for testing OpenID consumer implementations.
  \end{list}

\section{EXPERIENCE} 
  {\sl Full Time Programmer} -- \href{http://www.noomii.com}{Noomii Inc.} Vancouver, BC. \hfill \textbf{May 2009 - Present} \\
  \begin{itemize}
    \item Development of new features, test infrastructure and maintenance of Noomii.com using Ruby on Rails
  \end{itemize}

  {\sl Full Time Programmer} -- \href{http://www.mezine.com}{Mezine Inc.} Vancouver, BC. \hfill \textbf{Dec 2008 - Feb 2010} \\
  \begin{itemize}
    \item Development of a Wiki Application using an in-house Ruby framework (\href{http://wiki.with.us}{Wiki With Us})
  \end{itemize}

  {\sl Full Time Programmer} -- \href{http://www.hasmanydevelopers.com}{has\_many :developers} \hfill \textbf{Mar 2007 - Nov 2008} \\
  \hspace*{110pt} Caracas, Venezuela. \\
  \begin{itemize}
    \item Development of a Sugar Tracking System for Diabetics using Ruby on Rails (\href{http://www.sugarstats.com}{SugarStats})
    \item Development of Facebook and OpenID integration in an Enviromental Social Site using Merb. (\href{http://www.greenwala.com}{Greenwala})
    \item Development of a Multimedia System for Music Schools on the US using Ruby on Rails (\href{http://www.musiqbase.com}{MusiqBase})
    \item Development of an in-house OpenID Identity System (Client and Server) using Ruby on Rails
    \item Development of an application for parsing memorials pages to extract data using Ruby programming language with Hpricot 
    \item Development of features in a Web wedding planner application using Ruby on Rails. (\href{http://weddingbook.com/}{WeddingBook})
    \item Development of features in an Innovation Driven Community Web application using Ruby on Rails. (\href{http://www.ibridge.com}{iBridge})
  \end{itemize}

  {\sl Half Time Programmer} -- \href{www.terabrain.com}{Terabrain Communications}\hfill \textbf{Jul 2006 - Jan 2007}
  \hspace*{110pt} Caracas, Venezuela. \\
  \begin{itemize}
    \item Web Front-End for a cellular phone text messages client (SMS) using J2EE
  \end{itemize}

  {\sl Half Time Programmer} -- \href{www.ciens.ucv.ve/ccc}{CS School’s Computer Centre}\hspace{20pt} \textbf{Aug 2005 - Jan 2006}
  \hspace*{115pt} Universidad Central de Venezuela. \\
  \hspace*{115pt} Caracas, Venezuela. \\
  \begin{itemize}
    \item Web based printing application for the Computer Center using J2EE
  \end{itemize}
 
\section{REFERENCES} 
  Upon Request.



%
%\section{EXPERIENCE} {\textbf Business Applications Programmer} \hfill Fall 1990 \\
%                Allied-Signal Bendix Friction Materials Division, 
%                Financial Planning Department, Latham, NY
%                 \begin{itemize}  \itemsep -2pt % reduce space between items
%                 \item Developed four "user friendly" forecasting 
%                    systems each of which produces 18 to 139 
%                    individual reports. 
%                \item   Developed or improved almost all IFPS 
%                    programs used for financial reports. 
%                \end{itemize}
% 
%                {\textbf Research Programmer} \hfill            Summer 1990 \\
%                Psychology Department, Rensselaer Polytechnic 
%                Institute 
%                 \begin{itemize}  \itemsep -2pt %reduce space between items
%                 \item Performed computer aided statistical analysis 
%                    of data. 
%                 \end{itemize} 
%                {\textbf Assistant Manager} \hfill        Summers 1988-89 \\
%                Thunder Restaurant, Canton, CT
%                  \begin{itemize}
%                   \item Recognized need for, developed, and wrote 
%                    employee training manual. Performed various 
%                    duties including cooking, employee training, 
%                    ordering, and inventory control. 
%                   \end{itemize} 
% 
%\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
%                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
%                charity event to benefit the Troy Boys Club. Over 
%                250 people participated each year. 
%
%\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
%            Elected {\it House Manager}, Rho Phi Sorority \\
%            Elected {\it Sports Chairman} \\
%            Attended Krannet Leadership Conference \\
%                Headed delegation to Rho Phi Congress \\
%                Junior varsity basketball team \\
%                Participant, seven intramural athletic teams 
% 

\end{resume}
\end{document}







