% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Roman Gonzalez.}           % name for signature 
\longindentation=0pt                  % needed to get closing flush left
\let\raggedleft\raggedright           % needed to get date flush left
 
 
\begin{letter}{Dr. Andres L\"oh and Dr. Swierstra\\
Utrecht University \\
Utrecht, The Netherlands}


\begin{flushleft}
{\large\bf Roman Gonzalez}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 7707 Arthur Av. Burnaby, BC. Canada. V5J4G4 \\
\hfill +1 (604) 728-4864
\end{flushright} 

% \vspace{0.5in}
%\vfill % forces letterhead to top of page

 
\opening{Dear Dr. L\"oh and Dr. Swierstra:} 
 
\noindent I have been involved with Computer Sciences for the last 7 years. 
During that time I have achieved many goals including a Bachelor's degree in 
Computer Science with a specialization in Distributed Programming, honorable 
mentions granted by ACM and course certificates by IBM. I have participated and developed various Open 
Source projects and have worked with different businesses who use Ruby as their 
main language; I would like to enhance my skill set through learning the Haskell language.

\noindent Since my first interaction with Haskell in 2005, I have identified with the 
language and the functional programming paradigm in general. Because of this, I have spent the last two years
studying it from different sources such as technical books, university papers and websites. 
This, as helpful as it has been, has not been enough to gain a better understanding on the subject.

\noindent The Applied Functional Programming course seems to be the best option to fulfil my goal, given that this 
course is not only going to cover the Haskell language, but will also cover the theory behind it. This theory will help their participants to have better insight and understanding of the purpose of the many properties of Haskell. 

\noindent Students will receive lessons from two of the most notable professionals in the field, who through 
their publications have contributed significantly to the development of concepts, techniques and ideas on the functional
programming field. From these facts, it is clear that this course is the best way to be introduced to functional programming.

\noindent As time passes, the importance of the functional programming paradigm to solve problems of concurrent and distributed nature becomes more evident. As a developer who wants to work on the development of projects related to this area, a language like Haskell is a very important asset. This added to my affinity with the language, and the professors involved, makes this course a \emph{must} do.
 
\noindent Thank you for your consideration. I look forward to meeting both of you and other great developers, and to learning as much as I can about Haskell and functional programming in general.

Until then.

\closing{Best Regards.}

\end{letter}
 
\end{document}

